PANCHANGE_descriptives

### 2020-12-16 PANCHANGE_exclusion_descriptives.Rmd
added frequency tables for excluded dataset

>>>>

### pandemic change gad

```{r freq table gad perceived change}
dat %>%
  freq(gad.pandemic_felt_feelings)

```
### pandemic change phq

```{r freq table phq perceived change}

dat %>%
  freq(phq.pandemic_felt_feelings)

### Ethnicity
```{r freq table ethnicity}
dat %>%
  freq(Ethnicity_collapsed) 
```
### Gender
```{r freq table gender}
dat %>%
  freq(Gender_collapsed) 
```
### age categorical
```{r freq table age collapsed}
dat %>%
  freq(age_category_collapsed) 
```

### anxiety disorders
```{r freq table diagnosis anxiety}
dat %>%
  freq(anxiety_disorders) 
```

### Depressive disorders
```{r freq table diagnosis depression}
dat %>%
  freq(depressive_disorders) 
```
### Depression and anxiety
```{r freq table diagnosis depression and anxiety}
dat %>%
  freq(depression_and_anxiety) 
```
### Eating disorders
```{r freq table diagnosis eating disorder}
dat %>%
  freq(eating_disorders)

```
### OCD
```{r freq table diagnosis obsessive compulsive disorders}
dat %>%
  freq(obsessive_compulsive_disorders)

### Psychosis
```{r freq table diagnosis psychotic disorders}
dat %>%
  freq(psychotic_disorders)

### Bipolar
```{r freq table diagnosis bipolar}
dat %>%
  freq(mhd.mania_hypomania_bipolar_or_manicdepression)

### PTSD
```{r freq table diagnosis PTSD}
dat %>%
  freq(mhd.posttraumatic_stress_disorder_ptsd)

### ASD

```{r freq table diagnosis ASD}
dat %>%
  freq(autism_spectrum_disorder)

### ADHD
```{r freq table diagnosis ADHD}
dat %>%
  freq(mhd.attention_deficit_hyperactivity_disorder)

### Personality disorders
```{r freq table diagnosis personality disorder}
dat %>%
  freq(mhd.personality_disorder)

### Controls 
```{r freq table diagnosis control}
dat %>%
  freq(control) 
```
